### 2014-10-28 Neutral_simulPow.Rmd
Add paper figures & tables

Now I will simulate the model to Time=500 with a full set of parameters 
Replacement = 0,0.001,0.01,0.1,1 and ten repetitions

```{r simul256_LogSerParms, eval=F,echo=F,message=F,warning=F}
setwd("Simul")
#simul <- data.frame()
simul <- rbind(simul,simulNeutral_1Time(8,256,500))
simul <- rbind(simul,simulNeutral_1Time(64,256,500))
simul <- rbind(simul,simulNeutral_1Time(256,256,500))

```{r simul512_LogSerParms, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

simul <- rbind(simul,simulNeutral_1Time(8,512,500))
simul <- rbind(simul,simulNeutral_1Time(64,512,500))
simul <- rbind(simul,simulNeutral_1Time(256,512,500))

# rename s/'64'/'64_512'/ *neuFish64*.txt

@@

# Testing
#simul <- data.frame()
#sim1 <- rbind(simul,simulNeutral_1Time(65,256,100,"L",3))
#sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
#cc <- powerNeutral_1Time(simul[4,])

@@

pow_ADq24 <- data.frame()
comp_ADq24<- data.frame()
cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1Time(simul[i,],0.2, 0.04, 0.001) # Mortality,Dispersal,Colonization
}

for(i in 1:nrow(simul)) {
pow_ADq24 <- rbind(pow_ADq24, cc[[i]]$pow_AD)
comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
}
rm(cc)
pow_ADq24$MrtR <- 0.2
pow_ADq24$DspD <- 0.04
pow_ADq24$ClnR <- 0.001

@@

Mortality=0.2
Dispersal=0.4
Colonization=0.001

```{r power_LogSerParms1, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

#cc <- powerNeutral_1TimeParms(simul,0.2,0.4,0.001)

mm <- 0.2
dd <- 0.4
co <- 0.001

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1Time(simul[i,],mm, dd, co) # Mortality,Dispersal,Colonization
}
p_AD <- data.frame()

for(i in 1:nrow(simul)) {
	p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
}
rm(cc)
p_AD$MrtR <- mm
p_AD$DspD <- dd
p_AD$ClnR <- co

pow_ADq24 <- rbind(pow_ADq24, p_AD)

Mortality=0.4
Dispersal=0.04
Colonization=0.001

```{r power_LogSerParms2, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

mm <- 0.4
dd <- 0.04
co <- 0.001

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1Time(simul[i,],mm, dd, co) # Mortality,Dispersal,Colonization
}
p_AD <- data.frame()

for(i in 1:nrow(simul)) {
  	p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
}
rm(cc)
p_AD$MrtR <- mm
p_AD$DspD <- dd
p_AD$ClnR <- co

pow_ADq24 <- rbind(pow_ADq24, p_AD)

Mortality=0.4
Dispersal=0.4
Colonization=0.001

```{r power_LogSerParms3, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

mm <- 0.4
dd <- 0.4
co <- 0.001

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1Time(simul[i,],mm, dd, co) # Mortality,Dispersal,Colonization
}
p_AD <- data.frame()

for(i in 1:nrow(simul)) {
    p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
}
rm(cc)
p_AD$MrtR <- mm
p_AD$DspD <- dd
p_AD$ClnR <- co

pow_ADq24 <- rbind(pow_ADq24, p_AD)

stopCluster(cl)
rm(p_AD)
setwd(oldcd)
save.image()
```
# Make plots of power! using q=[-24,24]

I do not use simulations with ColonizationRate = 0.0001

Replace NumSp with spMeta=number of species in metacommunity

require(ggplot2)
pow_ADq24$MeanSp <- as.numeric(pow_ADq24$MeanSp)
pow_ADq24$power <- as.numeric(pow_ADq24$power)
pow_ADq24$typeI <- as.numeric(pow_ADq24$typeI)

# Add field with combination of dispersal & mortality 
pow_ADq24$DspMrt <- with(pow_ADq24,paste0(DspD," - ",MrtR))

# Add number of species in the metacommunity
pow_ADq24$spMeta <- ceiling(as.numeric(pow_ADq24$NumSp)*1.33)

g <- ggplot(pow_ADq24,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab("Metacommunity species number") +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="Disp - Mort")

g+theme_bw()
ggsave("powAD_spMeta_Side.png", width=6,height=6,units="in",dpi=600)

g <- ggplot(pow_ADq24,aes(x=MeanSp,y=typeI)) + geom_point(shape=19,aes(size=power,colour=DspMrt)) + facet_grid(Side ~ Type)
g+theme_bw()

# Recalculate power from comp_ADq24
#
require(plyr)
hh <-function(x) {
  t <- nrow(x)
  s <- nrow(x[x$p.value<0.05,])
  data.frame(power=s/t,n=t)
}

comp_ADq24$spMeta <- ceiling(as.numeric(comp_ADq24$NumSp)*1.33)

# Calculate power in fuction of replacement rate difference
# Falta cambiar NumSp por 
c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Type,DifR),hh)

g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)+
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab(bquote(Delta ~"Replacement rate")) +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="")

g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()

ggsave("powAD_DifReplacement.png", width=6,height=6,units="in",dpi=600)

require(pander)
pandoc.table(c2,style="grid")

# Calculate TypeI error in fuction of replacement rate
c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
names(c3)[4]<-"typeI"
g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
g+theme_bw()

rm(c1,c2,c3)

@@

```{r testAD_factors, eval=F,echo=F,message=T,warning=T}
require(plyr)
hh <-function(x) {
  t <- nrow(x)
  s <- nrow(x[x$p.value<0.05,])
  data.frame(count=s,power=s/t,n=t)
}
# Calculate power
c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Side,Type,MrtR1,DspD1,DifR),hh)
#require(dplyr)
#c2 <- tbl_df(c1)
#c3 <- c2 %>% 
#  group_by(NumSp,Side,Type,MrtR1,DspD1,DifR) %>% 
#  filter(p.value<0.05) %>% 
#  summarize(tot=n()) %>% 
#  summarize(pgt5=n()) 
model1 <-glm(count~NumSp*Side*Type*MrtR1*DspD1*DifR,poisson,data=c2)
summary(model1)
plot(model1)

@@

## Plot power of D1

require(ggplot2)
pow_TD1$MeanSp <- as.numeric(pow_TD1$MeanSp)
pow_TD1$power <- as.numeric(pow_TD1$power)
pow_TD1$typeI <- as.numeric(pow_TD1$typeI)
# Add number of species in the metacommunity
pow_TD1$spMeta <- ceiling(as.numeric(pow_TD1$NumSp)*1.33)

g <- ggplot(pow_TD1,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=Type)) + facet_grid(Side ~ . ) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab("Metacommunity species number") +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="")

g+theme_bw()

ggsave("powTD1_spMeta_Side.png", width=6,height=6,units="in",dpi=600)

g <- ggplot(pow_TD1,aes(x=spMeta,y=typeI)) + geom_point(shape=19,aes(size=power)) + facet_grid(Side ~ Type)
g+theme_bw()

# Recalculate power from comp_AD
#
require(plyr)
hh <-function(x) {
  t <- nrow(x)
  s <- nrow(x[x$p.value<0.05,])
  data.frame(power=s/t,n=t)
}

# Calculate power in fuction of replacement rate difference
# Falta cambiar NumSp por 
comp_TD1$spMeta <- ceiling(as.numeric(comp_TD1$NumSp)*1.33)

c1 <- with(comp_TD1,comp_TD1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))

c2 <- ddply(c1,.(spMeta,Type,DifR),hh)

g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( spMeta ~ .) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab(bquote(Delta ~"Replacement rate")) +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="")

g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()

ggsave("powTD1_DifReplacement.png", width=6,height=6,units="in",dpi=600)

# Calculate TypeI error in fuction of replacement rate
c1 <- with(comp_TD1,comp_TD1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
names(c3)[4]<-"typeI"
g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
g+theme_bw()

rm(c1,c2,c3)

@@

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,0,0,0.001)
}
pow_GC1 <- data.frame()
comp_GC1<- data.frame()

@@

require(ggplot2)
pow_GC1$MeanSp <- as.numeric(pow_GC1$MeanSp)
pow_GC1$power <- as.numeric(pow_GC1$power)
pow_GC1$typeI <- as.numeric(pow_GC1$typeI)

# Add number of species in the metacommunity
pow_GC1$spMeta <- ceiling(as.numeric(pow_GC1$NumSp)*1.33)

g <- ggplot(pow_GC1,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=Type)) + facet_grid(Side ~ . ) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab("Metacommunity species number") +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="") 
g+theme_bw()
ggsave("powGC_spMeta_Side.png", width=6,height=6,units="in",dpi=600)

# Recalculate power from comp_AD
#
require(plyr)
hh <-function(x) {
  t <- nrow(x)
  s <- nrow(x[x$p.value<0.05,])
  data.frame(power=s/t,n=t)
}

# Calculate power in fuction of replacement rate difference
comp_GC1$spMeta <- ceiling(as.numeric(comp_GC1$NumSp)*1.33)

c1 <- with(comp_GC1,comp_GC1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))

c2 <- ddply(c1,.(spMeta,Type,DifR),hh)

g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( spMeta ~ .) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab(bquote(Delta ~"Replacement rate")) +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="")

g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()

@@

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,40.2,0.0,0.001,10)
}
pow_GCq10 <- data.frame()
comp_GCq10<- data.frame()

@@

>>>>

Now I will simulate the model to Time=500 with a full set of parameters 
Replacement = 0,0.001,0.01,0.1,1 and 30 repetitions

```{r simul30_LogSerParms, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

simul <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
{
    simulNeutral_1Time(ps$nsp[i],ps$si[i],500,"L",30,F)
}
stopCluster(cl)

setwd(oldcd)
rm(ps,cn,cl)
save.image()

@@

# Testing
#
#simul <- data.frame()
#sim1 <- rbind(simul,simulNeutral_1Time(65,256,100,"L",3))
#sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
#cc <- powerNeutral_1Time(simul[4,])

mm <- 0.2
dd <- 0.04
co <- 0.001

@@

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1Time(simul[i,],mm, dd, co) # Mortality,Dispersal,Colonization
}
pow_ADq24 <- data.frame()
comp_ADq24<- data.frame()

for(i in 1:nrow(simul)) {
  pow_ADq24 <- rbind(pow_ADq24, cc[[i]]$pow_AD)
	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
}

rm(cc)

@@

@@

```{r testAD_factors, eval=F,echo=F,message=T,warning=T}
require(plyr)
hh <-function(x) {
  t <- nrow(x)
  s <- nrow(x[x$p.value<0.05,])
  data.frame(count=s,power=s/t,n=t)
}
# Calculate power
c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Side,Type,DifR),hh)
#require(dplyr)
#c2 <- tbl_df(c1)
#c3 <- c2 %>% 
#  group_by(NumSp,Side,Type,MrtR1,DspD1,DifR) %>% 
#  filter(p.value<0.05) %>% 
#  summarize(tot=n()) %>% 
#  summarize(pgt5=n()) 
model1 <-glm(count~NumSp*Side*Type*DifR,poisson,data=c2)
summary(model1)
plot(model1)

@@

```
Calculate Power using compareGrowthCurves and q=-24,24

@@

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,0.2,0.04,0.001)
}
pow_GC1 <- data.frame()
comp_GC1<- data.frame()

@@

setwd(oldcd)
rm(cc)
save.image()
```

@@

#] "0.2_0.04_0.001_1_1 3 0.2_0.04_0.001_1_3 3"
# Error: valor ausente donde TRUE/FALSE es necesario

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,0.2,0.04,0.001,10)
}
pow_GCq10 <- data.frame()
comp_GCq10<- data.frame()

@@

# Make plots of power! using q=[-24,24]

require(dplyr)
#pow_ADq24 <- with(pow_AD,pow_AD[MrtR==0.2 & DspD==0.04 & ClnR==0.001,])

# Select only the subset I will use
#
#pow_ADq24 <- filter(pow_AD,MrtR==0.2 & DspD==0.04 & ClnR==0.001) %>%
#  mutate(spMeta = ceiling(as.numeric(NumSp)*1.33))

plotPow_MeanSp_side(pow_ADq24)

ggsave("powADq24_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)

require(pander)
pandoc.table(select(pow_ADq24,Side,spMeta,MeanSp, c(5:9)),style="grid",split.tables=Inf)

pow_ADq24 <- pow_ADq24 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))

comp_ADq24 <- comp_AD %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
  left_join(unique(pow_ADq24[,1:3]),by=c("Side","NumSp"))

plotPow_MeanSp_difR(comp_ADq24)

ggsave("powADq24_DifReplacement.png", width=6,height=6,units="in",dpi=600)

# Calculate TypeI error in fuction of replacement rate
#c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
#c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
#names(c3)[4]<-"typeI"
#g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
#g+theme_bw()

#rm(c1,c2,c3)

```
## Plot power of D1

require(dplyr)

#pow_TD1$spMeta <- ceiling(as.numeric(pow_TD1$NumSp)*1.33)

pow_TD1 <- pow_TD1 %>% select(-MeanSp) %>% 
  mutate(spMeta=ceiling(as.numeric(NumSp)*1.33),power=as.numeric(power),typeI=as.numeric(typeI)) %>% 
  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))
require(pander)
pandoc.table(  select(pow_TD1,Side,spMeta,MeanSp,c(4:8)),style="grid",split.tables=Inf)

plotPow_MeanSp_side(pow_TD1)

ggsave("powTD1_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)

# Calculate power in fuction of replacement rate difference
# Falta cambiar NumSp por 
#comp_TD1$spMeta <- ceiling(as.numeric(comp_TD1$NumSp)*1.33)

pow_TD1 <- pow_TD1 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))

comp_TD1 <- comp_TD1 %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))

plotPow_MeanSp_difR(comp_TD1)
ggsave("powTD1_DifReplacement.png", width=6,height=6,units="in",dpi=600)

#pow_GC1 <-merge(pow_GC1,unique(pow_ADq10[,1:3]),by.x=c(1,2),by.y=c(1,2),all.y=F)[,c(1:2,10,4:9)]
#names(pow_GC1)[3]<- "MeanSp"
require(dplyr)

pow_GC1 <- pow_GC1 %>% select(-MeanSp) %>% 
  mutate(spMeta=ceiling(as.numeric(NumSp)*1.33),power=as.numeric(power),typeI=as.numeric(typeI)) %>% 
  left_join(unique(pow_ADq24[,1:3]),by=c("Side","NumSp")) %>%
  select(Side,spMeta,MeanSp,c(4:8))

require(pander)
pandoc.table(pow_GC1,style="grid",split.tables=Inf)

plotPow_MeanSp_side(pow_GC1)

ggsave("powGC_spMeta_Side.png", width=6,height=6,units="in",dpi=600)

plotPow_MeanSp_difR(comp_GC1)

```{r power_PlotADq10, eval=F,echo=F,message=T,warning=T}

#pow_GC1 <-merge(pow_GC1,unique(pow_ADq10[,1:3]),by.x=c(1,2),by.y=c(1,2),all.y=F)[,c(1:2,10,4:9)]
#names(pow_GC1)[3]<- "MeanSp"

plotPow_MeanSp_side(pow_ADq10)

ggsave("powADq10_MeanSp_Side.png", width=6,height=6,units="in",dpi=600)

## ADD ANOTHER COLUM WITH MEANSP
require(dplyr)
# DONE! in .RData
#
#pow_ADq10 <- pow_ADq10 %>% mutate(NumSp=as.numeric(NumSp),MeanSp=as.numeric(MeanSp),Side=as.numeric(Side))
#
#
#comp_ADq10 <- comp_ADq10 %>% filter(MrtR1==0.2 & DspD1==0.04 & ClnR1==0.001) %>% 
#  left_join(unique(pow_ADq10[,1:3]),by=c("Side","NumSp"))

plotPow_MeanSp_difR(comp_ADq10)

ggsave("powADq10_DifReplacement.png", width=6,height=6,units="in",dpi=600)

require(pander)
pandoc.table( mutate(pow_ADq10 ,spMeta=ceiling(as.numeric(NumSp)*1.33),power=as.numeric(power),typeI=as.numeric(typeI)) %>% select(Side,spMeta,MeanSp,c(5:9))
,style="grid",split.tables=Inf,round=4)
```

### 2014-10-28 SP_simul.Rmd
Add paper figures & tables

```{r simul_z1, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- compMethods_UniformSAD(8,256)

DqF <- rbind(DqF,compMethods_UniformSAD(64,256))

DqF <- rbind(DqF,compMethods_UniformSAD(256,256))

# Analizing this last it means that the scaling is broken at side 16
#  
#Dq2<- calcDq_multiSBA(fname1,"q.sed 16 1024 20 E",mfBin,T)
#Dq2$Type <- "rnzDqSAD16-512"
#Dq3<- rbind(Dq3,Dq2)
#
##Dq2<- calcDq_multiSBA(fname1,"q.sed 2 16 20 E",mfBin,T)
#Dq2$Type <- "rnzDqSAD2-16"
#Dq3<- rbind(Dq3,Dq2)
#plotDq(Dq3,"Type")

pandoc.table(DqF[DqF$R.Dq<0.8,],caption="R2<0.8")
setwd(oldcd)
```

@@

@@

@@

@@

setwd(oldcd)
rm(Dq1,Dq2,spa)

@@

```{r test_SAD256, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

@@

```{r power_adtest, eval=T,echo=F,message=F,warning=F}
# Check all simulations are present
require(plyr)
ddply(SadT,3:6,summarize, max(rep))
ddply(DqT,5:8,summarize, max(rep),min(rep))
powad <- data.frame()

@@

```{r power_adtest, eval=T,echo=F,message=F,warning=F}

@@

>>>>

```{r simul_z1, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- compMethods_UniformSAD(8,256)$Dq

DqF <- rbind(DqF,compMethods_UniformSAD(64,256)$Dq)

DqF <- rbind(DqF,compMethods_UniformSAD(256,256)$Dq)

# Analizing this last it means that the scaling is broken at side 16
#  
#Dq2<- calcDq_multiSBA(fname1,"q.sed 16 1024 20 E",mfBin,T)
#Dq2$Type <- "rnzDqSAD16-512"
#Dq3<- rbind(Dq3,Dq2)
#
##Dq2<- calcDq_multiSBA(fname1,"q.sed 2 16 20 E",mfBin,T)
#Dq2$Type <- "rnzDqSAD2-16"
#Dq3<- rbind(Dq3,Dq2)
#plotDq(Dq3,"Type")
require(pander)
pandoc.table(DqF[DqF$R.Dq<0.8,],caption="R2<0.8")
setwd(oldcd)
```

@@

DqF <- rbind(DqF,compMethods_UniformSAD(8,512))

@@

DqF <- rbind(DqF,compMethods_UniformSAD(256,512))

@@

For different number of species and different sides the same cualitative patterns are observed.

@@

@@

```{r test_SAD256, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

@@

```{r power_adtest, eval=F,echo=F,message=F,warning=F}
# Check all simulations are present
require(plyr)
ddply(SadT,3:6,summarize, max(rep))
ddply(DqT,5:8,summarize, max(rep),min(rep))
powad <- data.frame()

@@

```{r power_adtest, eval=F,echo=F,message=F,warning=F}

@@

## Plots for publication uniform SAD

```{r plots_spDq, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

# Plot of the uniform and randomized spatial pattern for a uniform SAD with 64 species and side=256
#

g <- plotSAD_SpatPat(64,256,"U")
g 
setwd("..")
ggsave("spat_Unif64_256.png", width=8,height=6,units="in",dpi=600)
setwd("Simul")

#
# Plots of Dq with uniform SAD and 20 repetitions!
#
unique(DqT$SAD)
#DqT$Type[DqT$Type=="SRS"] <- "DqSRS"
#DqT$Type[DqT$Type=="rnzSRS"] <- "rnzDqSRS"

rm(Dq1,Dq2,fname,fname1)

g <- plotDq_Side_Sp(DqT,256,64,"Uniform")
g
setwd("..")
ggsave("Dq_Unif64_256.png", width=8,height=4,units="in",dpi=600)

g <- plotDq_Side_Sp(DqT,256,0,"Uniform")
g
ggsave("Dq_Unif_NumSp_256.png", width=8,height=6,units="in",dpi=600)

g <- plotDq_Side_Sp(DqT,512,0,"Uniform")
g
ggsave("Dq_Unif_NumSp_512.png", width=8,height=6,units="in",dpi=600)

#
# Plot R2 for dqSAD dqSRS
#
g <- plotR2Dq_Side_Sp(DqT,256,64,"Uniform")
g
ggsave("R2Dq_Unif_64_256.png", width=8,height=6,units="in",dpi=600)

g <- plotR2Dq_Side_Sp(DqT,0,0,"Uniform")
g
ggsave("R2Dq_Unif_NumSp_Side.png", width=8,height=6,units="in",dpi=600)

#
# Generate Tables with R2 proportions
#
require(dplyr)
hh <-function(x,c,...){
  length(x[x>c])/length(x)
}

Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform",Side==256,NumSp==8,Type=="DqSAD")

Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform") %>%
  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Random","Regular")) %>%
  group_by(SAD,SpatialPattern,DqType,NumSp,Side) %>% 
  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9))

write.table(format(Dq1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)

#
# The same for neutral simulations with logseries metacommunity 
#

Dq1 <- filter(DqT, SAD=="Neutral" | SAD=="NeuUnif") %>%
  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Randomized","Unmodified")) %>%
  group_by(SAD,SpatialPattern,DqType,NumSp,Side) %>% 
  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9))

names(SadT)
Sad1 <- filter(SadT, SAD=="Neutral") %>%
  group_by(Type,Side,NumSp,SAD,rep) %>% summarize(NumSpAct=n()) %>% summarize(meanNumSp=mean(NumSpAct),rangeSp=paste(range(NumSpAct),collapse="-"))

# Merge Sad1 with Dq1 for meanNumSp
unique(Sad1$Type)
unique(Dq1$DqType)
Dq1 <- inner_join(Dq1,Sad1) %>% select(SAD, meanNumSp,Side,SpatialPattern,DqType,Freq60,Freq90)
pow <- distinct(select(pow_ADq24,NumSp,spMeta))

Dq1 <- left_join(Dq1,pow)  %>% 
    select(SAD, spMeta,meanNumSp,Side,SpatialPattern,DqType,Freq60,Freq90)
names(Dq1)
write.table(format(Dq1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)

rm(Dq1,Sad1,pow)

#
# plot of the Fit of the method for Dq
#

setwd("Simul")

zq <- readDq_fit(256,64,"Uniform")
g <- plotDqFitG(zq)
g
setwd(oldcd)
ggsave("DqFit_Unif_64_256.png", width=8,height=6,units="in",dpi=600)

g <- plotDqFitGQ(zq,c(-10,-4,-1,0,1,4,10))
g

## Plots for publication Logseries SAD

```{r plots_logser_spDq, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

# Plot of the uniform and randomized spatial pattern for a logseries SAD with 64 species and side=256
#

#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! GENERA MAL 
# save_matrix_as_sed
# 
# Le falta un \n

g <- plotSAD_SpatPat(64,256,"L")
g 
setwd("..")
ggsave("spat_Logser64_256.png", width=8,height=6,units="in",dpi=600)

unique(DqT$SAD)

g <- plotDq_Side_Sp(DqT,256,64,"Logseries")
g
ggsave("Dq_Logser64_256.png", width=8,height=4,units="in",dpi=600)

g <- plotDq_Side_Sp(DqT,256,0,"Logseries")
g
ggsave("Dq_Logser_NumSp_256.png", width=8,height=6,units="in",dpi=600)

g <- plotDq_Side_Sp(DqT,512,0,"Logseries")
g
ggsave("Dq_Logser_NumSp_512.png", width=8,height=6,units="in",dpi=600)

#
# Plot R2 for dqSAD dqSRS
#
g <- plotR2Dq_Side_Sp(DqT,256,64,"Logseries")
g
ggsave("R2Dq_Logser_64_256.png", width=8,height=6,units="in",dpi=600)

g <- plotR2Dq_Side_Sp(DqT,0,0,"Logseries")
g

#
# plot of the Fit of the method for Dq
#

setwd("Simul")

zq <- readDq_fit(256,64,"Logseries")
g <-plotDqFitG(zq)
g
setwd(oldcd)
ggsave("DqFit_Logser_64_256.png", width=8,height=6,units="in",dpi=600)
